---
title: "Crime"
author: "Raghav S & Vedant Shah"
date: "2023-05-21"
output:
  pdf_document: default
  html_document: default
---

## 1)Loading the dataset
```{r}
data <- read.csv("D:/Sem 6/EDA/Crimes_-_2001_to_Present_refined.csv")
```

This command is used to load the dataset to perform various R operations on it.

## 2)Installing a package
```{r}
library(ggplot2)
```

This command installs the "ggplot2" package that contains all the plots and other functions.

## 3)Constructing a Histogram
```{r}
ggplot(data,aes(x=Beat))+geom_histogram()
```

This command constructs a histogram by taking in the ID variable as input.

## 4)Constructing a Histogram with different properties
```{r}
ggplot(data,aes(x=Beat))+geom_histogram(fill="white",color="black")
```

This command constructs a histogram by taking in the ID variable as input and changing the color properties of the histogram.

## 5)Constructing a Kernel Density Plot
```{r}
ggplot(data,aes(x=Beat))+geom_density()
```

This command constructs a kernel density plot by taking in the Beat variable as input.

## 6)Constructing a Boxplot
```{r}
ggplot(data,aes(x=Beat))+geom_boxplot()
```

This command constructs a boxplot by taking in the Beat variable as input.

## 7)Constructing a Bar Plot
```{r}
ggplot(data,aes(y=Beat))+geom_bar()
```

This command constructs a kernel bar plot by taking in the Beat and Beat variables as input.

## 8)Constructing a Stair Step Plot
```{r}
ggplot(data,aes(x=ID,y=Beat))+geom_step()
```

This command constructs a stair step plot by taking in the ID and Beat variables as input.

## 9)Counting the number of observations
```{r}
ggplot(data,aes(x=ID,y=Beat))+geom_count()
```

This command counts the number of observations.

## 10)Constructing a Crossbar Plot
```{r}
ggplot(data,aes(x=ID,y=Beat))+geom_area()
```

This command constructs a crossbar plot by taking in the ID and Beat variables as input.

## 11)Constructing a Line Plot
```{r}
ggplot(data,aes(x=ID,y=Beat))+geom_line()
```

This command constructs a line plot by taking in the ID and Beat variables as input.

## 12)Constructing a Blank Plot
```{r}
ggplot(data,aes(x=ID))+geom_blank()
```

This command constructs a blank plot by taking in the ID variable as input.

## 13)Constructing a Scatter Plot
```{r}
idv = data[["ID"]]
bv = data[["Beat"]]
plot(x=idv,y=bv)
```

This command constructs a scatter plot by taking in the ID and Beat variables as input.

## 14)Constructing a Bubble Plot
```{r}
ggplot(data,aes(x=ID,y=Beat))+geom_point()
```

This command constructs a bubble plot by taking in the ID and Beat variables as input.

## 15)Constructing a Scatter Plot with fitted values
```{r}
ggplot(data, aes(x = ID, y = Beat)) +
        geom_point() +
        stat_smooth(method = "lm",
        col = "#C42126", se = FALSE, size = 1
)
```

This command constructs a scatter plot with fitted values by taking in the ID and Beat variables as input.